Macros for straightforward parallelism in Clojure

### 2016-04-22 paper/paper.Rnw
asd

\section{Related Work} \label{label:related_work}
% only discuss task based parallelism in this section
Clojure has access to all of the JVM, so it has access to the Java \code{ForkJoinPool} library\cite{Lea2000}.
The \code{ForkJoinPool} library allows Java programmers to create lightweight, recursive tasks which are executed by a thread pool.
Each thread maintains a queue of tasks to work on.
When a thread runs out of tasks, it steals tasks from other threads.
Work stealing has been used a scheduling mechanism is a variety of modern threading libraries and has been very successful \cite{Lea2000, Blumofe1994, Blumofe1995a}
Users of a \code{ForkJoinPool} create a subclass of \code{RecursiveTask} to compute the value of some function.
Each of these tasks may create more \code{RecursiveTask}s, submit them to the \code{ForkJoinPool}, then wait for their subtasks to complete, without blocking the pool.
Clojure programmers can use the \code{ForkJoinPool} libraries from Clojure, but the interface isn't exactly programmer friendly (or idiomatic).

>>>>

\section{Related Work} \label{label:related_work}
% only discuss task based parallelism in this section
Clojure has access to all of the JVM, so it has access to the Java \code{ForkJoinPool} library\cite{Lea2000}.
The \code{ForkJoinPool} library allows Java programmers to create lightweight, recursive tasks which are executed by a thread pool.
Each thread maintains a queue of tasks to work on.
When a thread runs out of tasks, it steals tasks from other threads.
Work stealing has been used as a scheduling mechanism isn a variety of modern threading libraries and has been very successful \cite{Lea2000, Blumofe1994, Blumofe1995a}
Users of a \code{ForkJoinPool} create a subclass of \code{RecursiveTask} to compute the value of some function.
Each of these tasks may create more \code{RecursiveTask}s, submit them to the \code{ForkJoinPool}, then wait for their subtasks to complete, without blocking the pool.
Clojure programmers can use the \code{ForkJoinPool} libraries from Clojure, but the interface isn't exactly programmer friendly (or idiomatic).
